Changes From Preregistration

### 2021-07-14 preregistration_changes.rmd
- implemented major changes after feedback from reviewers

# Theoretical Background
## Hypotheses

 -	We've changed the order of the hypotheses.
 -	We've changed the wording of the hypotheses (but not the content)
    -	Before: “H1: People are more likely to communicate actively on the website, the less they are concerned about their privacy.”
    - Now: “H1: People are more likely to self-disclose on a website when they are less concerned about their privacy.”
 -  We've changed the enumeration of the hypotheses (but not the overall number). 
    - Before, hypotheses were enumerated from 1-13.
    - Now, it's 1, 2, 3, 4, 5a, 5b, 5c, 5d, 6a, 6b, 6c, 7a, 7b.

>>>>

# Theoretical Background

In general, instead of analyzing _self-disclosure_, we're now analyzing communication behavior. Before, we tried to operationalized self-disclosure with the log of communication frequency plus likes and dislikes. However, we realized that this operationalization is too coarse to represent self-disclosure. We now analyze the mere quantity of communication, which is much less debatable.

## Hypotheses

 -	We've changed the order of the hypotheses.
 -	We've changed the wording of the hypotheses (but not the content).
 -  We've changed the enumeration of the hypotheses. 
    - Before, hypotheses were enumerated from 1-13.
    - Now, it's 1, 2, 3, 4, 5a, 5b, 5c, 5d, 6a, 6b, 6c, 7a, 7b.

## Research Question

 -  We dropped two Research Questions, because we realized that they just didn't make sense. That is, we dropped the RQ that popularity cues might affect self-efficacy and trust
